\Title

### 2011-04-04 masters_thesis/proposal/proposal.tex
Finalized proposal based on feedback from the committee

Particle swarm optimization (PSO) is an evolutionary algorithm that has proven
effective at solving complicated optimization problems.  Since its inception,
however, PSO has been run primarily in serial on a single machine.  With the
world's computing resources increasingly coming from large clusters of
processors, the parallelization of the algorithm is important to its continued
relevance.  PSO has previously been parallelized primarily by distributing the
computation corresponding to particles across multiple processors.  In these
approaches, additional processors can only add more particles to the swarm.
However, in many cases this is not efficient when scaled to very large swarm
sizes (on very large clusters).  Current methods cannot answer well the
question, ``What do you do with 1000 processors when 50 or 100 particles is the
most efficient swarm size?''  In this project we attempt to answer that
question with a speculative approach to the parallelization of PSO motivated by
speculative execution in modern computer hardware.

@@

When many processors are available, a speculative approach to the
parallelization of PSO can yield dramatic improvements in the performance of
the algorithm on expensive functions compared to previous parallelization
techniques.

@@

\item March 11, 2011: Finish running experiments and incorporate the results
  into the thesis.

\item March 15, 2011: Give final draft of thesis to advisor for review.

\item March 22, 2011: submit thesis to second committee member for review.

\item April 5, 2011: submit thesis to third committee member for review.

\item April 19, 2011: defend thesis.

>>>>

Particle swarm optimization (PSO) is an evolutionary algorithm that has proven
effective at solving complicated optimization problems.  In this project we
present a speculative approach to the parallelization of PSO motivated by
speculative execution in modern computer hardware.

@@

When many processors are available, a speculative approach to the
parallelization of particle swarm optimization can yield dramatic improvements
in the performance of the algorithm on expensive functions compared to previous
parallelization techniques.

@@

\item May 13, 2011: Finish running experiments and start incorporating the
  results into the thesis.

\item May 30, 2011: Give final draft of thesis to advisor for review.

\item June 10, 2011: submit thesis to second committee member for review.

\item June 30, 2011: submit thesis to third committee member for review.

\item July 15, 2011: defend thesis.
